\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
\markboth{Abstract}{Abstract}

\noindent The \textit{Donation Platform with Payment Gateway} is designed to modernize the process of charitable giving by ensuring transparency, efficiency, and security. Traditional donation methods often face challenges such as lack of accountability, geographical limitations, and inefficient fund tracking. This project addresses these issues by providing an intuitive, web-based platform where **donors, NGOs, and companies** can seamlessly interact. NGOs can create and manage fundraising campaigns, donors can contribute securely through a **Cashfree payment gateway**, and companies can evaluate and support charitable initiatives as part of their Corporate Social Responsibility (CSR) efforts.  

Leveraging the **MERN (MongoDB, Express.js, React.js, Node.js) stack**, the platform ensures scalability, real-time transaction processing, and robust security measures. A **role-based access control system** is implemented to define permissions for Admins, NGOs, and Companies, ensuring data integrity and restricted access to sensitive information. The backend handles **user authentication, campaign management, and donation tracking**, while APIs facilitate secure and efficient interactions between system components.  

Comprehensive testing using **Postman** ensures the reliability of API responses, while the real-time transaction monitoring system enhances transparency. The platform provides **detailed donation reports and campaign analytics**, allowing stakeholders to track contributions effectively. By integrating advanced web technologies, the project enhances digital philanthropy by making online donations more accessible, secure, and trustworthy.  

\noindent\textbf{Keywords:} Online Donation, Payment Gateway, MERN Stack, NGO Fundraising, Digital Philanthropy, Role-Based Access Control.
