\chapter{System Requirements Specification}

\section{Introduction}
The System Requirements Specification (SRS) defines the functional and non-functional requirements for the **Donation Platform with Payment Gateway Integration**. This chapter outlines the system’s purpose, scope, user roles, and the detailed technical and operational requirements.

\section{System Overview}
The proposed system is a **MERN stack-based donation platform** that enables NGOs and companies to manage fundraising campaigns while allowing donors to contribute seamlessly. The system ensures **transparency, security, and efficiency** in handling donations.

\subsection{Scope of the System}
The system will provide:
\begin{itemize}
    \item Role-based access control for **Admin, NGOs, Companies, and Donors**.
    \item Secure online donation processing via **Cashfree payment gateway**.
    \item A campaign management system for NGOs to create and monitor donation drives.
    \item A dashboard with real-time donation tracking and reporting.
    \item Secure authentication using **JWT-based token system**.
    \item A scalable backend API with **MongoDB database** for structured data storage.
\end{itemize}

\section{Functional Requirements}
The functional requirements define the core features of the donation platform.

\subsection{User Roles and Permissions}
The system will support four types of users, each with distinct permissions.

\begin{itemize}
    \item \textbf{Admin}
    \begin{itemize}
        \item Manage users (approve/disable NGOs, Companies).
        \item Manage and verify campaigns.
        \item Access donation and activity reports.
        \item Modify or delete campaigns in case of policy violations.
    \end{itemize}

    \item \textbf{NGOs}
    \begin{itemize}
        \item Register and manage NGO profile.
        \item Create, update, and track donation campaigns.
        \item Accept and manage received donations.
        \item Access campaign reports and donor details.
    \end{itemize}

    \item \textbf{Companies}
    \begin{itemize}
        \item View NGO profiles and available campaigns.
        \item Donate to campaigns and receive tax exemption receipts.
        \item Access their donation history.
    \end{itemize}

    \item \textbf{Donors (Public Users)}
    \begin{itemize}
        \item Browse campaigns and make donations.
        \item Get transaction receipts via email.
        \item View donation impact reports.
    \end{itemize}
\end{itemize}

\subsection{Authentication and Security}
\begin{itemize}
    \item Users must register and log in using **email and password authentication**.
    \item **JWT-based authentication** will be implemented for secure API access.
    \item Passwords will be securely stored using **bcrypt hashing**.
\end{itemize}

\subsection{Campaign Management}
\begin{itemize}
    \item NGOs can **create, update, and delete** fundraising campaigns.
    \item Each campaign must include **title, description, goal amount, end date, and images**.
    \item Admin has the right to approve or reject campaigns.
\end{itemize}

\subsection{Payment Processing}
\begin{itemize}
    \item The platform will integrate the **Cashfree payment gateway** for secure transactions.
    \item Donations can be made via **UPI, credit/debit cards, and net banking**.
    \item Real-time tracking of donations and campaign progress will be available.
\end{itemize}

\subsection{Donation Reporting and Analytics}
\begin{itemize}
    \item NGOs and Admin can view donation reports with **amounts, donor details, and timestamps**.
    \item Companies can generate reports for tax exemption purposes.
    \item Campaign analytics will show the **funding progress, donor count, and trends**.
\end{itemize}

\section{Non-Functional Requirements}
These requirements define system performance, security, and usability aspects.

\subsection{Performance Requirements}
\begin{itemize}
    \item The system should handle **simultaneous transactions without downtime**.
    \item Response time for critical actions (donations, logins) should be **under 2 seconds**.
\end{itemize}

\subsection{Security Requirements}
\begin{itemize}
    \item Secure communication using **HTTPS and SSL encryption**.
    \item Protection against **SQL injection, CSRF, and XSS attacks**.
    \item Regular **database backups** to prevent data loss.
\end{itemize}

\subsection{Usability Requirements}
\begin{itemize}
    \item A **mobile-responsive UI** for ease of access.
    \item **Intuitive dashboard** for campaign tracking and donor insights.
\end{itemize}

\subsection{Scalability Requirements}
\begin{itemize}
    \item The system should support **thousands of concurrent users**.
    \item The backend should be scalable using **Node.js and MongoDB cluster**.
\end{itemize}

\section{System Architecture Overview}
The system follows a **MERN stack (MongoDB, Express.js, React.js, Node.js) architecture**.

\begin{itemize}
    \item **Frontend:** React.js for a dynamic UI.
    \item **Backend:** Express.js (Node.js) for API handling.
    \item **Database:** MongoDB for scalable document storage.
    \item **Payment Gateway:** Cashfree for transaction processing.
    \item **Authentication:** JWT for secure role-based access control.
\end{itemize}
