\chapter{Introduction}

\section{Background}
Charitable giving plays a crucial role in addressing social issues, but traditional donation processes often lack transparency, accessibility, and efficiency. Many donors hesitate to contribute due to concerns about fund misuse, while NGOs struggle with limited outreach and resource constraints. To overcome these challenges, digital donation platforms have emerged as a reliable solution, enabling secure transactions, streamlined management, and global reach.  

This project, \textbf{"Donation Platform with Payment Gateway"}, is designed to facilitate seamless interactions between **donors, NGOs, and companies** by providing a structured, transparent, and secure online donation system. The platform integrates role-based access control and real-time transaction tracking, ensuring that funds are utilized effectively.  

\section{Problem Statement}
The current donation system faces several challenges:
\begin{itemize}
    \item Lack of **transparency** in fund utilization, making donors hesitant to contribute.
    \item **Limited accessibility** for NGOs to reach potential donors beyond geographical constraints.
    \item **Inefficient manual processes** for tracking and managing donations.
    \item **Security risks** in online transactions, including fraud and unauthorized access.
    \item **Absence of a unified platform** for companies to evaluate and support NGO initiatives.
\end{itemize}

To address these challenges, our system provides a **secure, automated, and easy-to-use online donation platform** that enhances trust and convenience for all stakeholders.

\section{Objectives}
The primary objectives of this project are:
\begin{itemize}
    \item To develop a **web-based donation platform** that connects donors with NGOs securely.
    \item To integrate a **secure payment gateway (Cashfree)** for real-time donation transactions.
    \item To implement **role-based access control** for:
        \begin{itemize}
            \item **Admin** – Manage NGOs, campaigns, and monitor transactions.
            \item **NGO** – Create and manage fundraising campaigns.
            \item **Company** – Evaluate and support NGO campaigns.
            \item **Donor** – Can directly donate from the website.
        \end{itemize}
    \item To provide **real-time tracking and reporting** of donations for transparency.
    \item To ensure **scalability and security** by using the **MERN stack (MongoDB, Express.js, React.js, Node.js)**.
\end{itemize}

\section{Scope of the Project}
The **Donation Platform with Payment Gateway** is designed to:
\begin{itemize}
    \item Enable NGOs to create and manage campaigns with complete details.
    \item Allow donors to contribute via multiple payment methods securely.
    \item Provide **admin monitoring** with insights into donation reports and user activities.
    \item Ensure **role-based data access** to prevent unauthorized modifications.
    \item Enhance transparency through **publicly accessible campaign details**.
\end{itemize}

The project focuses on **developing a fully functional prototype**, with future possibilities of integrating **blockchain for fund tracking, AI-based donor recommendations, and multilingual support**.

\section{Methodology}
The project follows a **structured software development methodology**, including:
\begin{itemize}
    \item **Requirement Analysis** – Identifying user needs and system functionalities.
    \item **System Design** – Creating data flow diagrams, wireframes, and database models.
    \item **Development** – Implementing the backend using **Node.js and Express.js**, the frontend using **React.js**, and the database using **MongoDB**.
    \item **Integration & Testing** – Using **Postman for API testing** and ensuring security through authentication methods.
    \item **Deployment** – Hosting the platform on a cloud-based service.
\end{itemize}

\section{Significance of the Project}
This project provides a **trustworthy and efficient** alternative to conventional donation methods, benefiting:
\begin{itemize}
    \item **Donors** – By offering transparency and secure payment options.
    \item **NGOs** – By expanding outreach and managing funds digitally.
    \item **Companies** – By simplifying CSR (Corporate Social Responsibility) contributions.
\end{itemize}

\section{Report Organization}
This document is structured as follows:
\begin{itemize}
    \item \textbf{Chapter 1: Introduction} – Provides an overview of the project, objectives, and problem statement.
    \item \textbf{Chapter 2: Literature Review} – Discusses existing donation platforms and their limitations.
    \item \textbf{Chapter 3: System Requirements Specification} – Defines functional and non-functional requirements.
    \item \textbf{Chapter 4: System Design} – Covers architectural design, data models, and technology stack.
    \item \textbf{Chapter 5: Methodology} – Explains the development approach and process.
    \item \textbf{Chapter 6: Implementation} – Describes development steps, API functionalities, and payment integration.
    \item \textbf{Chapter 7: Results and Discussion} – Presents system performance, test cases, and evaluation.
    \item \textbf{Chapter 8: Evaluation} – Analyzes key findings based on testing.
    \item \textbf{Chapter 9: Conclusion} – Summarizes the findings.
    \item \textbf{Chapter 10: Future Work} – Suggests potential improvements and enhancements.
\end{itemize}
