\chapter{Methodology}

\section{Introduction}
This chapter outlines the structured approach followed in the development of the **Donation Platform with Payment Gateway**. The methodology consists of multiple phases, including **requirement gathering, system design, development, testing, and deployment**. The development follows the **Agile methodology**, ensuring iterative improvements and real-time feedback integration.

\section{Research and Requirement Analysis}
The first phase involved a **detailed analysis** of the problem statement and requirements of various stakeholders, including **NGOs, donors, and administrators**. A **comparative study of existing donation platforms** was conducted to identify gaps and areas for improvement.

\subsection{Primary Data Collection}
\begin{itemize}
    \item Interviews with NGO representatives to understand their challenges.
    \item Surveys among donors to analyze donation preferences and security concerns.
    \item Review of payment gateway providers to choose the most reliable and secure integration.
\end{itemize}

\subsection{Secondary Data Collection}
\begin{itemize}
    \item Analysis of existing donation platforms such as **GoFundMe, Milaap, and Ketto**.
    \item Research on secure online payment processing using **Cashfree Payment Gateway**.
    \item Study of **MERN stack best practices** for scalable web applications.
\end{itemize}

\section{Software Development Methodology}
The **Agile Software Development Lifecycle (SDLC)** was adopted, allowing iterative development with continuous improvements based on user feedback.

\subsection{Phases of Agile SDLC}
\begin{enumerate}
    \item \textbf{Planning:} Defining system scope, identifying modules, and selecting appropriate technologies.
    \item \textbf{Requirement Analysis:} Finalizing functional and non-functional requirements.
    \item \textbf{Design:} Creating architectural diagrams, database schemas, and UI wireframes.
    \item \textbf{Development:} Implementing features in **MERN stack**, ensuring modularity.
    \item \textbf{Testing:} Conducting **unit testing, integration testing, and user acceptance testing (UAT)**.
    \item \textbf{Deployment:} Hosting the platform on **cloud infrastructure** with security configurations.
    \item \textbf{Maintenance & Enhancements:} Continuous monitoring, bug fixes, and feature upgrades.
\end{enumerate}

\section{System Implementation Approach}
The implementation follows a **modular approach**, where different system components are developed independently and integrated later.

\subsection{Backend Development (Node.js & Express.js)}
\begin{itemize}
    \item Implementation of **RESTful APIs** for authentication, campaign management, donations, and reporting.
    \item Database modeling using **MongoDB**, ensuring efficient data storage and retrieval.
    \item Integration of **JWT-based authentication** for secure access control.
\end{itemize}

\subsection{Frontend Development (React.js)}
\begin{itemize}
    \item UI development using **React.js and Material UI** for a responsive design.
    \item API integration with backend services using **Axios**.
    \item Role-based dashboards for **Admins, NGOs, and Donors**.
\end{itemize}

\subsection{Payment Gateway Integration}
\begin{itemize}
    \item Integration of **Cashfree Payment Gateway** for seamless transactions.
    \item Implementation of **transaction tracking, status updates, and receipt generation**.
    \item Secure handling of financial transactions using **encryption protocols**.
\end{itemize}

\subsection{Security Measures}
\begin{itemize}
    \item Implementation of **bcrypt** for password hashing.
    \item Role-based access control (RBAC) for **Admin, NGO, and Donor** accounts.
    \item Secure API endpoints using **JWT authentication**.
\end{itemize}

\section{Testing Strategy}
To ensure the reliability of the system, multiple levels of testing were conducted:

\subsection{Unit Testing}
\begin{itemize}
    \item Individual modules were tested using **Jest and Mocha**.
    \item APIs were validated with **Postman** to check request-response consistency.
\end{itemize}

\subsection{Integration Testing}
\begin{itemize}
    \item Ensured proper interaction between **frontend and backend** components.
    \item Verified secure data transmission during **user authentication and payment processing**.
\end{itemize}

\subsection{User Acceptance Testing (UAT)}
\begin{itemize}
    \item Conducted testing with a **focus group of NGOs and donors**.
    \item Feedback collected for UI/UX improvements and security enhancements.
\end{itemize}

\section{Deployment and Maintenance}
\subsection{Deployment Plan}
The system was deployed using **cloud infrastructure**, ensuring high availability.

\begin{itemize}
    \item Backend deployed on **AWS EC2 / DigitalOcean**.
    \item Frontend hosted on **Vercel / Netlify**.
    \item Database hosted on **MongoDB Atlas**.
\end{itemize}

\subsection{Maintenance and Future Enhancements}
\begin{itemize}
    \item Continuous monitoring using **logging and analytics tools**.
    \item Periodic security audits to detect vulnerabilities.
    \item Future enhancements include **AI-based fraud detection for donations**.
\end{itemize}
